Floral choice

### 2020-12-18 analyses/floral_choice.Rmd
developed sweet visitation bias analysis

# Load packages
```{r message=FALSE, warning=FALSE, include=FALSE, echo = FALSE}
library(vegan)
library(ggvegan)
library(ggrepel)
library(treemapify)
library(mgcv)
library(mgcViz)
library(rstatix)
library(tidyverse)
library(lubridate)
library(patchwork)
library(tidymodels)
```

@@

visited.siteyear <- net %>%
  group_by(site, plant.sp, year) %>%
  summarize(visits = n())

@@

auxilliary_data.visits <- net %>%
  group_by(site, year) %>%
  summarize(sample.dates = length(unique(date)),
            bb.abund = n())

@@

families.visits <- net %>% 
  group_by(plant.family, site) %>%
  summarize(visits = n()) %>%
  group_by(site) %>%
  mutate(visit.prop = visits/sum(visits))

families <- full_join(families.survey, families.visits) %>%
  select(plant.family, site,  survey.prop, visit.prop) %>%
  replace_na(replace = list(survey.prop = 0, visit.prop = 0)) %>%
  mutate(representation.fold = (visit.prop - survey.prop)/survey.prop, # representation as fold-change
         representation = visit.prop - survey.prop) %>%
  ungroup()

@@

aov.fam <- aov(representation ~ plant.family, data = families)
aov.fam.test <- anova_test(aov.fam)
aov.fam.tuk <- tukey_hsd(aov.fam)

aov.fam2 <- aov(representation.fold ~ plant.family, data = filter(families, !is.infinite(representation.fold)))
aov.fam2.test <- anova_test(aov.fam2)
aov.fam2.tuk <- tukey_hsd(aov.fam2)

@@

morphotypes.visits <- net %>% 
  group_by(k.type.ss, site) %>%
  summarize(visits = n()) %>%
  group_by(site) %>%
  mutate(visit.prop = visits/sum(visits),
         k.type.ss = factor(k.type.ss))

morphotypes <- full_join(morphotypes.survey, morphotypes.visits) %>%
  select(k.type.ss, site,  survey.prop, visit.prop) %>%
  replace_na(replace = list(survey.prop = 0, visit.prop = 0)) %>%
  mutate(representation.fold = (visit.prop - survey.prop)/survey.prop, # representation as fold-change
         representation = visit.prop - survey.prop) %>%
  ungroup()

@@

aov.morph <- aov(representation ~ k.type.ss, data = morphotypes)
aov.morph.test <- anova_test(aov.morph)
aov.morph.tuk <- tukey_hsd(aov.morph)

aov.morph2 <- aov(representation.fold ~ k.type.ss, data = filter(morphotypes, !is.infinite(representation.fold)))
aov.morph2.test <- anova_test(aov.morph2)
aov.morph2.tuk <- tukey_hsd(aov.morph2)

library(brms)
brm.morph <- brm(representation ~ k.type.ss, data = morphotypes)
```

>>>>

# Load packages
```{r message=FALSE, warning=FALSE, include=FALSE, echo = FALSE}
library(vegan)
library(ggvegan)
library(ggrepel)
library(treemapify)
library(mgcv)
library(mgcViz)
library(rstatix)
library(brms)
library(tidyverse)
library(lubridate)
library(patchwork)
library(tidymodels)
```

@@

visited.siteyear <- net %>%
  filter(caste != "male") %>%
  group_by(site, plant.sp, year) %>%
  summarize(visits = n())

@@

auxilliary_data.visits <- net %>%
  filter(caste != "male") %>%
  group_by(site, year) %>%
  summarize(sample.dates = length(unique(date)),
            bb.abund = n())

@@

families.visits <- net %>% 
  filter(caste != "male") %>%
  group_by(plant.family, site) %>%
  summarize(visits = n()) %>%
  group_by(site) %>%
  mutate(visit.prop = visits/sum(visits))

families <- full_join(families.survey, families.visits) %>%
  select(plant.family, site,  survey.prop, visit.prop) %>%
  replace_na(replace = list(survey.prop = 0, visit.prop = 0)) %>%
  mutate(representation.fold = (visit.prop - survey.prop)/survey.prop, # representation as fold-change
         representation = visit.prop - survey.prop) %>%
  group_by(plant.family) %>%
  mutate(survey.prop.norm = scale(survey.prop),
         visit.prop.norm = scale(visit.prop)) %>%
  ungroup() %>%
  left_join(site_data)

@@

brm.fam <- brm(representation ~ plant.family, data = families)
plot(brm.fam)
plot(marginal_effects(brm.fam))
hist(resid(brm.fam))
mcmc_plot(brm.fam, type = "intervals")

@@

morphotypes.visits <- net %>% 
  filter(caste != "male") %>%
  group_by(k.type.ss, site) %>%
  summarize(visits = n()) %>%
  group_by(site) %>%
  mutate(visit.prop = visits/sum(visits),
         k.type.ss = factor(k.type.ss))

morphotypes <- full_join(morphotypes.survey, morphotypes.visits) %>%
  select(k.type.ss, site,  survey.prop, visit.prop) %>%
  replace_na(replace = list(survey.prop = 0, visit.prop = 0)) %>%
  mutate(representation.fold = (visit.prop - survey.prop)/survey.prop, # representation as fold-change
         representation = visit.prop - survey.prop) %>%
  group_by(k.type.ss) %>%
  mutate(survey.prop.norm = scale(survey.prop),
         visit.prop.norm = scale(visit.prop)) %>%
  ungroup() %>%
  left_join(site_data)

@@

brm.morph <- brm(representation ~ k.type.ss, data = morphotypes)
plot(brm.morph)
plot(marginal_effects(brm.morph))
hist(resid(brm.morph))
mcmc_plot(brm.morph, type = "intervals", pars = c("b_k.type.ss1", "b_k.type.ss2", "b_k.type.ss3",
                                                  "b_k.type.ss4", "b_k.type.ss5", "b_k.type.ss6",
                                                  "b_k.type.ss7", "b_k.type.ss8", "b_k.type.ss9",
                                                  "b_k.type.ss10"))
mcmc_plot(brm.morph, type = "intervals")

### By elevation
ggplot(families, aes(elev.mean, representation)) +
  geom_point() +
  geom_smooth() +
  facet_wrap(~plant.family)

ggplot(families, aes(elev.mean, visit.prop)) +
  geom_point() +
  geom_smooth() +
  facet_wrap(~plant.family)

ggplot(families, aes(elev.mean, visit.prop.norm)) +
  geom_point() +
  geom_smooth() +
  facet_wrap(~plant.family)

ggplot(families, aes(elev.mean, survey.prop)) +
  geom_point() +
  geom_smooth() +
  facet_wrap(~plant.family)

ggplot(families, aes(elev.mean, survey.prop.norm)) +
  geom_point() +
  geom_smooth() +
  facet_wrap(~plant.family)

ggplot(morphotypes, aes(elev.mean, representation)) +
  geom_point() +
  geom_smooth() +
  facet_wrap(~k.type.ss)

ggplot(morphotypes, aes(elev.mean, visit.prop)) +
  geom_point() +
  geom_smooth() +
  facet_wrap(~k.type.ss)

ggplot(morphotypes, aes(elev.mean, visit.prop.norm)) +
  geom_point() +
  geom_smooth() +
  facet_wrap(~k.type.ss)

ggplot(morphotypes, aes(elev.mean, survey.prop)) +
  geom_point() +
  geom_smooth() +
  facet_wrap(~k.type.ss)

ggplot(morphotypes, aes(elev.mean, survey.prop.norm)) +
  geom_point() +
  geom_smooth() +
  facet_wrap(~k.type.ss)
```

# Do BB species differ in their taxonomic/phylogenetic/morphological biases? And how does this vary with elevation/time?
```{r}
morphotypes.visits_sp <- net %>% 
  group_by(k.type.ss, site, bb.sp) %>%
  summarize(visits = n()) %>%
  group_by(site, bb.sp) %>%
  mutate(visit.prop = visits/sum(visits))

sp_by_site <- net %>%
  ungroup() %>%
  select(site, bb.sp) %>%
  distinct()

morphotypes_sp1 <- full_join(morphotypes.survey, morphotypes.visits_sp)

morphotypes_never_visited <- filter(morphotypes_sp1, is.na(bb.sp)) %>%
  select(-bb.sp) %>%
  left_join(sp_by_site) %>%
  replace_na(replace = list(visits = 0, visit.prop = 0))

morphotypes_sp <- full_join(morphotypes.survey, morphotypes.visits_sp) %>%
  filter(!is.na(bb.sp)) %>%
  bind_rows(morphotypes_never_visited) %>%
  select(k.type.ss, site, bb.sp, survey.prop, visit.prop) %>%
  replace_na(replace = list(survey.prop = 0, visit.prop = 0)) %>%
  mutate(representation.fold = (visit.prop - survey.prop)/survey.prop, # representation as fold-change
         representation = visit.prop - survey.prop) %>%
  group_by(k.type.ss, bb.sp) %>%
  mutate(survey.prop.norm = scale(survey.prop),
         visit.prop.norm = scale(visit.prop)) %>%
  ungroup() %>%
  left_join(site_data)

ggplot(filter(morphotypes_sp, bb.sp %in% c("pasc", "prat", "bss", "wurf", "soro", "psit", "hort")), 
       aes(elev.mean, representation, color = bb.sp)) +
  geom_line() +
  #geom_smooth() +
  facet_wrap(~k.type.ss)
```
